Tensor anisotropy as a tracer of cosmic voids

### 2015-05-26 RefereeResponse.md

    Response: 
    - The requested histogram has been added as the bottom panel of Fig. 2. This shows that lower values of
      the FA are associated to small (voids) and large values (clusters) of the density.

More minor things:
==

7. **I'm confused a bit about the middle panels of Fig. 1. The title,
    "Visual impresion for lambda_th=..."  is strange. Aren't there
    several thresholds here? Also, what are the blue dots? Also
    "impresion" is  misspelled.**

    Response:
    - We have rewritten the caption. There are two different
    thresholds, one for each web finder. Blue dots were dark matter
    halos (FOF). We removed them for clarity. The typo ("impresion")
    is  also corrected.

### 2015-05-26 cosmic_voids.tex
solved issue #17, caption in Figure 1

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Visual impression of different fields in a slice of
    $1\hMpc$ width in the Bolshoi simulation.   
    Fractional Anisotropy field (left); cosmic web classification
    (middle) where voids are white, sheets are light gray, filaments
    are dark gray and knots are black; individual voids (right) found by 
    the a watershed algorithm on the Fractional Anisotropy field. Colours
    correspond with the effective radius of each void. Top/bottom
    corresponds to the T-Web/V-Web.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

>>>>

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Different fields in a slice of
    $1\hMpc$ width in the Bolshoi simulation. Top/bottom panels correspond
    to the T-Web/V-Web.      
    Fractional Anisotropy field (left); cosmic web classification
    (middle) for a given value of the threhold eigenvalue
    $\lambda_{\rm th}$ where voids are white, sheets are light gray,
    filaments are dark gray and knots are black; individual voids (right) found by 
    the a watershed algorithm on the Fractional Anisotropy field. Colours
    in the right panels correspond with the effective radius of each void. }
  \label{fig:FA_field}
\end{figure*}
%.........................................................................
